---
title: "Homework 1"
author: Hanyu Lu
output: github_document
---

This is my solution to HW1.

```{r}
library(tidyverse)
library(ggplot2)
```


## Problem 1

Create a data frame with the specified elements.

```{r}
prob1_df=
  tibble(
    samp = rnorm(10),
    samp_gt_0 = samp > 0,
    char_vec = c("a", "b", "c", "d", "e", "f", "g", "h", "i", "j"),
    factor_vec = factor(c("low", "low", "low", "mod", "mod", "mod", "mod", "high", "high", "high"))
  )
```

Take the mean of each variable in my data frame.

```{r}
mean(pull(prob1_df, samp))
mean(pull(prob1_df, samp_gt_0))
mean(pull(prob1_df, char_vec))
mean(pull(prob1_df, factor_vec))
```

I can take the mean of numbers and logical but not character or factor.

```{r eval=FALSE}
as.numeric(pull(prob1_df, samp))
as.numeric(pull(prob1_df, samp_gt_0))
as.numeric(pull(prob1_df, char_vec))
as.numeric(pull(prob1_df, factor_vec))
```

I have numerical outputs for numbers, logical, and factor variables, but not for characters.
Mean does not exist for any variables not converted to numerical values.

```{r}
as.numeric(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.factor(pull(prob1_df, samp_gt_0)) * pull(prob1_df, samp)
as.numeric(as.factor(pull(prob1_df, samp_gt_0))) * pull(prob1_df, samp)
```

After factors are converted to numbers, they can do arithmetic operations including multiplication.  However, factors are not eligible for multiplication.

## Problem 2

First, load the penguins dataset.

```{r}
data("penguins", package = "palmerpenguins")
```

* There are several variables in the penguins dataset that includes `r ls(penguins)`.
Among those variables, bill_length_mm has range ( `r range(penguins$bill_length_mm, na.rm = TRUE)` ), bill_depth_mm has range ( `r range(penguins$bill_depth_mm, na.rm = TRUE)` ), flipper_length_mm has range ( `r range(penguins$flipper_length_mm, na.rm = TRUE)` ), year has range ( `r range(penguins$year, na.rm = TRUE)` ), body_mass_g has range ( `r range(penguins$body_mass_g, na.rm = TRUE)` ), sex has levels `r levels(penguins$sex)`, species has levels `r levels(penguins$species)`, and island has levels `r levels(penguins$island)`.

* The dataset has `r nrow(penguins)` rows and `r ncol(penguins)` columns.

* The mean flipper length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`.

* Make a scatterplot of flipper length (y) vs bill length (x) with points colored in accordance with different species.

```{r warning = FALSE}
ggplot(penguins, aes(x = flipper_length_mm, y = bill_depth_mm, color = species)) + geom_point()
ggsave("first_scatterplot_hl3439.png")
```

